---
title: "Language profile preschoolers with 22q11DS"
output: ""
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## R Markdown

This script produces the outcomes reported in [paper X]

R version 4.0.2 (2020-06-22)
Platform: x86_64-w64-mingw32/x64 (64-bit)
Running under: Windows 8.1 x64 (build 9600)

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] effectsize_0.4.4-1 broom_0.7.1        ppcor_1.1          MASS_7.3-51.6      expss_0.10.6       pastecs_1.3.21     forcats_0.5.0      stringr_1.4.0     
 [9] purrr_0.3.4        readr_1.4.0        tibble_3.0.3       tidyverse_1.3.0    e1071_1.7-3        rstatix_0.6.0      ggpubr_0.4.0       tidyr_1.1.2       
[17] dplyr_1.0.2        ggplot2_3.3.2      readxl_1.3.1      

loaded via a namespace (and not attached):
 [1] httr_1.4.2         jsonlite_1.7.1     carData_3.0-4      modelr_0.1.8       assertthat_0.2.1   blob_1.2.1         cellranger_1.1.0   bayestestR_0.9.0  
 [9] yaml_2.2.1         pillar_1.4.6       backports_1.1.10   glue_1.4.2         digest_0.6.25      ggsignif_0.6.0     checkmate_2.0.0    rvest_0.3.6       
[17] colorspace_1.4-1   htmltools_0.5.0    pkgconfig_2.0.3    haven_2.3.1        scales_1.1.1       openxlsx_4.2.3     rio_0.5.16         htmlTable_2.1.0   
[25] generics_0.0.2     car_3.0-10         ellipsis_0.3.1     withr_2.3.0        cli_2.0.2          magrittr_1.5       crayon_1.3.4       evaluate_0.14     
[33] fs_1.5.0           fansi_0.4.1        xml2_1.3.2         foreign_0.8-80     class_7.3-17       tools_4.0.2        data.table_1.13.0  hms_0.5.3         
[41] lifecycle_0.2.0    matrixStats_0.57.0 munsell_0.5.0      reprex_0.3.0       zip_2.1.1          compiler_4.0.2     rlang_0.4.7        grid_4.0.2        
[49] parameters_0.13.0  rstudioapi_0.11    htmlwidgets_1.5.2  rmarkdown_2.8      boot_1.3-25        gtable_0.3.0       abind_1.4-5        DBI_1.1.0         
[57] curl_4.3           R6_2.4.1           lubridate_1.7.9    knitr_1.30         utf8_1.1.4         insight_0.13.2     stringi_1.5.3      Rcpp_1.0.5        
[65] vctrs_0.3.4        dbplyr_1.4.4       tidyselect_1.1.0   xfun_0.18

```{r}
# Clear workspace:
rm(list=ls())

## load packages
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggpubr) 
library(rstatix)
library(e1071)
library(tidyverse)
library(pastecs)
library(expss)
library(ppcor)
library(effectsize)
```
#Variables
Subject (numerical)   = anonymous subject ID 
AgeMd   (numerical)   = age in months
AgeYd   (numerical)   = age in years
Sex     (numerical)   = numerical dummy for sex, 1=female, 2=male
IQ      (numerical)   = Intelligence Quotient, age normed score, range 55 - 145, M = 100, SD = 15
SES     (numerical)   = Socioeconomic status, here: parental education on a scale from 1-9 based in Dutch education system, see categories below.
FstWord (numerical)   = numerical dummy for category age of first word, see answer categories below
FstSent (numerical)   = age in months
PPVT    (numerical)   = WBQ score of the Peabody Picture Vocabulary Test, age normed score, range 55 - 145, M = 100, SD = 15 
#CELF Preschool-2-NL, age normed score, range 55 - 145, M = 100, SD = 15
 KS      (numerical)   = Core Language Index score of the C. Subtests
 RTI     (numerical)   = CELF Preschool-2-NL 
 ETI     (numerical)   = CELF Preschool-2-NL
#
 ZB      (numerical) 
 WS      (numerical) 
 AW      (numerical) 
 BAV     (numerical) 
 ZH      (numerical) 
 EC      (numerical) 
 WC.R    (numerical) 
LogoV   (numerical) 


SES categories (in Dutch)
Both mother and father were asked the highest completed level of education based on these categories: 
1.	Geen opleiding (lager onderwijs: niet afgemaakt)
2.	Lager onderwijs (lagere school, basisschool, speciaal basisonderwijs)
3.	Lager of voorbereidend beroepsonderwijs (zoals huishoudschool, vbo, lbo, lts, leao, lhno, vmbo)
4.	Middelbaar algemeen voortgezet onderwijs (zoals mavo, (m)ulo, ivo, vmbo-t)
5.	Mbo 2 of 3 jaar
6.	Middelbaar beroepsonderwijs en beroepsbegeleidend onderwijs (zoals mbo 4 jaar, mts, meao, mhno, bol, bbl, in(t)as)
7.	Hoger algemeen en voorbereidend wetenschappelijk onderwijs (zoals havo, vwo, atheneum, gymnasium, hbs, mms)
8.	Hoger beroepsonderwijs (zoals hbo, hts, heao, hhno)
9.	Wetenschappelijk onderwijs (universiteit, hbo master)


First Word / Sentence
Parents were asked "How old was your child when it spoke its first word/sentence?"
Word                                                Sentences 
1 = no words yet                                    1 = no sentences yet, 
2 = younger than most children (<10 months)         2 = younger (<18 months) 
3 = same age (11-15 months)                         3 = same age (19-24 months)
4 = slightly older (16-24 months)                   4 = slightly older (25-30 months) 
5 = older (> 25 months)                             5 = older (> 31 months)


LogoV inversion
Label                                    Original         New
 Normal                                     0              5
 Different from other children's speech,
    but not enough to cause comment         1              4
 Different enough to provoke comment, 
    but possible to understand most speech  2              3
 Only just intelligible to strangers        3              2
 Impossible to understand                   4              1
 
 
```{r}
## set working directory
setwd("C:/Users/Emma/Documents/Thuis werken/good-enough-project-template/data/processed")

## load data
data <- read_excel("Datafile_repo.xlsx") #this data has been generated at random 

### inverting LogoV scores 0-4 to 5-1 (LogoV 0 = new 5, 1 = 4, 2 = 3, 3 = 2, 4 = 1)
data$LogoV <- 5-data$LogoV


### Dataframes ###
dataIndexP <- data[c("Subject", "PPVT", "KS", "RTI", "ETI")] 
dataERTI <- data[c("Subject", "RTI", "ETI")]
dataSubtest <- data[c("Subject", "ZB", "AW", "ZH", "WS", "BAV", "EC", "WC.R")]
dataIndexLogoV <- data[c("Subject", "PPVT", "KS", "RTI", "ETI", "LogoV")]
IndexPdata <- data[c("Subject","AgeMd", "Sex", "SES", "LogoV", "KS", "ETI", "RTI", "PPVT")] #missing data demographic comparison
dataTask_Missing <- data[c("Subject", "PPVT", "ZB", "AW", "ZH", "WS", "BAV", "EC", "WC.R")]

# Long format
tidydataSubtest <- dataSubtest %>% gather(Task, Score, -c(Subject))
tidydataIndexP <- dataIndexP %>% gather(Index, Score, -c(Subject))
tidydataIndexLogoV <- dataIndexLogoV %>% gather(Index, Score, -c(Subject, LogoV))
tidydataERTI <- dataIndexP %>% gather(Index, Score, -c(Subject))

# For missing data comparison
IndexPdata_comp <- IndexPdata[complete.cases(IndexPdata), ]
dataERTI_comp <- dataERTI[complete.cases(dataERTI), ]
ExcludedIndexP <- subset(IndexPdata, is.na(ETI) == TRUE | is.na(RTI) == TRUE | is.na(KS) == TRUE | is.na(PPVT) == TRUE)
```
 
 
 c
 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
